Conservation decision-making under long transients

### 2019-08-12 slides/solarized.Rmd
tweaks

# Decisions vs transient dynamics: what could possibly go wrong?

@@

<div style='float:left;width:50%'>
  <img src='img/city-mit-license.jpg' style='transform:translate(-20%, -10%);height:100%;object-fit:cover;overflow:hidden'>
</div>

@@

<div style='float:left;width:50%'>
  <img src='img/royalsociety/pensive-polarbear.jpg' style='transform:translate(-20%, -10%);height:900px;overflow:hidden'>
</div>

@@

@@

- Given time-series observations, can we distinguish ghost attractors from real attractors?

@@

Hierarchical Bayesian estimation of stability using TensorFlow(R)

@@

@@

# Descision Theory
### Management under uncertainty
.pull-left[

@@

@@

.pull-left[
## Outbreak

![](img/flickr-vsmoothe-pine-beetle.jpg)

- manage at acceptable/endemic level?
- supress entirely?

@@

**Incorrect belief of bistable system**

@@

**Incorrect belief of stronger bistable system**

@@

**Mistaken ghost for alternate stable state**:

@@

```{r}
```

@@

- Lizzie Wolkovich
- Henry Scharf

>>>>

# What could possibly go wrong?

@@

<div style='float:left;width:50%'>
  <img src='img/city-slice.jpeg' style='transform:translate(-22%, -10%);height:100%;object-fit:cover;overflow:hidden'>
</div>

@@

<div style='float:left;width:50%'>
  <img src='img/royalsociety/pensive-polarbear-slice.jpg' style='transform:translate(-22%, -10%);height:990px; width:1329; overflow:hidden'>
</div>

@@

<img src="img/royalsociety/pensive-polarbear.jpg" width="400", style="float:center">

@@

Given time-series observations, *can we distinguish* **ghost** attractors from **real** ones?

@@

Hierarchical Bayesian estimation of stability

@@

Using TensorFlow(R) via `greta` R package, <https://greta-stats.org>

@@

(Full ensemble 500 length-3000 replicate timeseries)

```{r}
samples3 <- read_csv("../data/posterior_ensemble.csv.xz")
samples3 %>%  
  ggplot() + 
  geom_histogram(aes(value), bins = 30, col=txtcolor)  +
  geom_vline(aes(xintercept = 0.023), col = pal[1], lwd = 2)

---
background-image: url(img/royalsociety/gentoo-penguin.jpg)
background-position: left
background-size: 140%
class: center, top

# Descision Theory

# Descision Theory

@@

---
class: middle

@@

---
background-image: url(img/royalsociety/forest-fire.jpg)
background-position: center
background-size: 120%
class: center, top

---
background-image: url(img/royalsociety/methane_bubbles.jpg)
background-position: center
background-size: 100%
class: center, top

---
background-image: url(img/flickr-vsmoothe-pine-beetle.jpg)
background-position: center
background-size: 100%
class: center, top

@@

## Incorrect belief of bistable system

@@

## Incorrect belief of stronger bistable system

@@

## Mistaken ghost for alternate stable state

@@

```{r eval=FALSE}
sim <- readRDS("sim-ghost-learning-2.Rds")

 sim$posterior %>% 
  data.frame(time = 1:Tmax) %>%
  filter(time %in% seq(1,Tmax, by = 5)) %>%
  gather(param, probability, -time, factor_key =TRUE) %>% 
  mutate(param = as.numeric(param)) %>% 
  ggplot(aes(param, probability, group = time, alpha = time)) + 
  geom_bar()

library(patchwork)
p1 + p2
```

@@

![](img/noaa.png)

Lizzie Wolkovich

Henry Scharf
